Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-30 automatica/paper.tex
added identification to the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our benchmark suite consists of 27 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.

The \textit{acrobot} plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2} and \textit{Chen\_ex3} benchmarks 
correspond to high-order control system discrete models generally used as 
case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
\textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} are 
automotive cruise control models. Automotive cruise control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, 
compensating disturbances and uncertainties related to relief and terrain.

There are two continuous stirred tank reactor models named \textit{cstr} and 
\textit{cstrtmp}, which describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
dynamics of a basic brushed direct current electrical machine.

The \textit{Flexbeam} benchmark is a plant employed in vibration studies; the 
physical  system consists of a flexible metallic structure with piezoceramic 
actuators and sensors. The \textit{guidance chen} benchmark is another 
high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
model order reduction techniques; it corresponds to a guidance control system model,
which is used to determine the path of an autonomous vehicle movement. The 
\textit{helicopter} benchmark plant describes the dynamics of transitional motion 
with respect to a longitudinal plane and the rotational motion around the longitudinal 
axis for a coaxial helicopter.

The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass, which must be equilibrated above the pivot point and is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

The \textit{magpointer} corresponds to a magnetic pointer plant composed by a pointer 
employed in analogue gauges and indicators, whose angular position dynamics is 
controlled by a magnetic field. The \textit{magsuspension} describes the dynamic of
a magnetic car suspension system. The \textit{pendulum} plant consists of a swinging 
point mass suspended from a frictionless pivot by means of a negligible mass rod.

The \textit{Regulator} plant consists of a linear model of a synchronous electrical
machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant is a classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &   &  &  &  & & & &\\
2  & Antenna  & 6 &   &  &  &  & & & &\\
3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & & & &\\
5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & &\\
6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
7  & Chen\_ex3 & 7 &   & & & & & & &\\
8  & Chen\_ex4 & 9 &  & & & & & & &\\
9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms &  & & &\\
10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
12 & Cstr & 1 & &  & & & & & &\\
13 & Cstrtmp  & 1 &   &  & & & & & &\\
14 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
15 & Flexbeam   & 6 &   &  & & & & & &\\
16 & Guidance chen  & 5 &   &  & & & & & &\\
17 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
18 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
19 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
20 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
21 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
22 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
23 & Regulator   & 5 &   &  & & & & & &\\
24 & Springmassdamper & 2 &   &  & & & & & &\\
25 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
26 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
27 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

Our benchmark suite consists of 26 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.

The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark (\#4) is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
benchmarks (\#5-8) correspond to high-order control system discrete models generally used as 
case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
\textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) are 
automotive cruise control models. Automotive cruise control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, 
compensating disturbances and uncertainties related to relief and terrain.

There are two continuous stirred tank reactor models named \textit{cstr} (\#11) and 
\textit{cstrtmp} (\#12), which describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a basic brushed direct current electrical machine.

The \textit{Flexbeam} benchmark (\#14) is a plant employed in vibration studies; the 
physical  system consists of a flexible metallic structure with piezoceramic 
actuators and sensors. The \textit{guidance chen} benchmark (\#15) is another 
high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
model order reduction techniques; it corresponds to a guidance control system model,
which is used to determine the path of an autonomous vehicle movement. The 
\textit{helicopter} benchmark plant (\#16) describes the dynamics of transitional motion 
with respect to a longitudinal plane and the rotational motion around the longitudinal 
axis for a coaxial helicopter.

The benchmarks \textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18)
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass, which must be equilibrated above the pivot point and is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

The \textit{magpointer} (\#19) corresponds to a magnetic pointer plant composed by a pointer 
employed in analogue gauges and indicators, whose angular position dynamics is 
controlled by a magnetic field. The \textit{magsuspension} describes (\#20) the dynamic of
a magnetic car suspension system. The \textit{pendulum} (\#21) plant consists of a swinging 
point mass suspended from a frictionless pivot by means of a negligible mass rod.

The \textit{Regulator} (\#22) plant consists of a linear model of a synchronous electrical
machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant (\#23) is a classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark (\#24) describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} (\#25) benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark (\#26)
corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &   &  &  &  & & & &\\
2  & Antenna  & 6 &   &  &  &  & & & &\\
3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & & & &\\
5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & &\\
6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
7  & Chen\_ex3 & 7 &   & & & & & & &\\
8  & Chen\_ex4 & 9 &  & & & & & & &\\
9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms &  & & &\\
10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
11 & Cstr & 1 & &  & & & & & &\\
12 & Cstrtmp  & 1 &   &  & & & & & &\\
13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
14 & Flexbeam   & 6 &   &  & & & & & &\\
15 & Guidance chen  & 5 &   &  & & & & & &\\
16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
22 & Regulator   & 5 &   &  & & & & & &\\
23 & Springmassdamper & 2 &   &  & & & & & &\\
24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
26 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
